An Accurate Model for SARS-CoV-2 pooled RT-PCR Test Errors

### 2021-03-30 comment.tex
equal contibutions

\author[1,2]{Yair Daon}
\author[2,3,*]{Amit Huppert}
\author[1,2,*]{Uri Obolski}

\affil[1]{Porter School of the Environment and Earth Sciences, The
  Faculty of Exact Sciences, Tel Aviv University\\ Tel Aviv, Israel}

\affil[2]{School of Public Health, The Faculty of Medicine, Tel Aviv
  University\\ Tel Aviv, Israel}

>>>>

\author[1,2]{Yair Daon}
\author[1,3,*]{Amit Huppert}
\author[1,2,*]{Uri Obolski}

\affil[1]{School of Public Health, The Faculty of Medicine, Tel Aviv
  University\\ Tel Aviv, Israel}

\affil[2]{Porter School of the Environment and Earth Sciences, The
  Faculty of Exact Sciences, Tel Aviv University\\ Tel Aviv, Israel}
